---
title: "Mini Frac Analysis Report"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document: default
  html_document:
    df_print: paged
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Input Data
```{r}
                                    data <- df_input_en()
                                    knitr::kable(data, col.names = NULL)
                                    br()
```

### Mini-Frac test
```{r fig.width = 9, fig.height = 5}
df_inject = df_inject_en()
  # df_inject <-read_excel("minifrac_test.xlsx")
  colnames(df_inject)<-c('t','u', 'p', 'V', 'g')
  
  fig <- plot_ly()
  # Add traces
  fig <- fig %>% add_trace(x = ~df_inject$t, y = ~df_inject$u, name = "Bottomhole Injection rate, m3/min", mode = "lines+markers", type = "scatter", 
                           line = list(color = 'rgb(60, 77, 233)'), marker = list(color = 'rgb(60, 77, 233)'))
  
  m <- list(
    l = 70,
    r = 70,
    b = 50,
    t = 10,
    pad = 10
  )
  
  ay <- list(color = "rgb(233, 16, 16)",
             overlaying = "y",
             side = "right",
             title = list(text ="Bottomhole Pressure, atm", standoff = 20))
  
  fig <- fig %>% add_trace(df_inject, x = ~df_inject$t, y = ~df_inject$p, name = "Bottomhole Pressure, atmм", yaxis = "y2", mode = "lines+markers", type = "scatter",
                           line = list(color = 'rgb(233, 16, 16)'), marker = list(color = 'rgb(233, 16, 16)'))
  
  # Set figure title, x and y-axes titles
  fig <- fig %>% layout(
    yaxis2 = ay,
    xaxis = list(title="Time, min"),
    yaxis = list(title="Bottomhole Injection rate, m3/min", color ='rgb(60, 77, 233)')
  )%>%
    layout(plot_bgcolor='#e5ecf6',
           xaxis = list(
             zerolinecolor = '#ffff',
             zerolinewidth = 2,
             gridcolor = 'ffff'),
           yaxis = list(
             zerolinecolor = '#ffff',
             zerolinewidth = 2,
             gridcolor = 'ffff'),
           margin = m,
           # legend = list(x = 0.01, y = 0.9),
           showlegend = FALSE
    )
  
  fig 
```

## Calculation theory

The concept of pressure curve analysis is based on the observation that the degree of pressure drop during fracture closure contains useful information about the intensity of the leakoff process. 

Fracture volume:
$$V_{t_e}=V_i-2A_eS_p-2A_eg\left(\Delta t_D,\alpha\right)C_L\sqrt{t_e}$$
where the dimensionless time interval $\Delta t_D=\Delta t/t_e$; $V_i$ - pumped volume for one fracture wing; 
$g\left(\Delta t_D,\alpha\right)$ - Grasgof function (g-function)

In the PKN model, the constant $\alpha$ is assumed to be $\frac{4}{5}$.

Approximation of the g-function for a given value $\alpha$:
$$g\left(d,\frac{4}{5}\right)=\frac{1,41495+79,4125d+632,457d^2+1293,07d^3+763,19d^4+94,0367d^5}{1+54,8534d^2+383,11d^3+540,342d^4+167,741d^5+6,49129d^6}$$
where $d$ – dimensionless time

The proportionality coefficient $S_f$, or fractute stiffness, for the PKN model:
$$S_f=\frac{2E^\prime}{\pi h_f}$$
Plane strain modulus: 
$$E^\prime=\frac{E}{1 -\nu^2}$$
The linear trend of the g-function: 
$$p=b_N-m_N\times g\left(\Delta t_D,\alpha\right)$$
where $b_N$ is the intersept coefficient of the straight line, atm; $m_N$ is the slope coefficient, atm.

Apparent leakoff coefficient (for total area): 
$$C_L=\frac{-m_N}{2\sqrt{t_e}S_f}$$
Leakoff coefficient in permeable layer 
$$C_{L, \; res}=C_L\cdot\frac{1}{r_p}$$
$$r_p = \frac{h_p}{h_f}$$
Fracture half length:
$$x_f=\frac{2E^\prime V_i}{\pi h_f^2\left(b_N-p_c\right)}$$
Average fracture width:
$$\bar{w_e}=\frac{V_i}{x_fh_f}-2g_0\left(\alpha\right)C_L\sqrt{t_e}$$
Fluid efficiency: 
$$\eta_e=\frac{x_f\cdot\bar{w_e}\cdot h_f}{V_i}$$





### Mini-frac analysis results
```{r}
                                    data <- df_result_en()
                                    colnames(data)<-c('Parameter','Value')
                                    knitr::kable(data)
                                     br()
```

### g-function plot


```{r fig.width = 8, fig.height = 5}
    df = df_g_en()
    # df_inject <-read_excel("minifrac_test.xlsx")
    colnames(df)<-c('g','p', 'lin')
    
    fig <- plot_ly()
    # Add traces
    fig <- fig %>% add_trace(x = ~df$g, y = ~df$p, name = "Pressure, atm", mode = "markers", type = "scatter", 
                             marker = list(color = '#3131E1', size = 9))


    fig <- fig %>% add_trace(x = ~df$g, y = ~df$lin, name = "Linear trend", mode = "lines", type = "scatter",
                             line = list(color = '#27AE60', size = 7))
    # 
    # Set figure title, x and y-axes titles
    fig <- fig %>% layout(
      xaxis = list(title="g-function"),
      yaxis = list(title="Pressure, atm", range = c(0,800))
    )%>%
      layout(plot_bgcolor='#e5ecf6',
             xaxis = list(
               zerolinecolor = '#ffff',
               zerolinewidth = 2,
               gridcolor = 'ffff'),
             yaxis = list(
               zerolinecolor = '#ffff',
               zerolinewidth = 2,
               gridcolor = 'ffff'),
             # legend = list(x = 0.01, y = 0.9),
             showlegend = FALSE
      )
    fig  
```

### Report comment
```{r Interval2, warning = FALSE}
note_in_md_word(input$markdowninput_en)
```
